Chemical tagging can work: \\ Identification of stellar phase-space structures \\ purely by chemical-abundance similarity\vspace{-7ex}

### 2016-08-06 papers/kmeans/response_to_referee.txt

    This paper presents new element abundance results using The
    Cannon, a novel, powerful method for spectroscopic abundance
    measurements. The results presented in this paper are new and
    very much relevant to the many large scale observing projects
    that are currently in operation.

    I highlight some comments for the authors to address:

    Abstract: The last sentence is not true, as the authors note
    later in the text the first blind search purely in abundance
    space was carried out by Mitschang et al 2014.

We have referenced Mitschang et al (2014) for their work in chemical
tagging, but we believe the last sentence of the abstract is
correct. To clarify: Mitschang et al (2014) did perform a blind
search in chemical abundances to identify substructure, but one of the
key conclusions of their work was that ".. these groups may not
represent distinct formation sites, e.g. as in dissolved open
clusters, as previously thought". While the Mitschang et al (2014)
work showed their chemically-identified structures had similar (U, V,
W) space velocities (e.g., their Figure 2), those velocities are not
dissimilar from the background velocity distribution. In contrast, our
work is the first blind search in chemical abundances that has
identified structures that are *also* structures in phase-space:
specifically on-sky position and radial velocities.

@@

This statement and point is true and wise. We have modified the text
in [HOGG]

    Section 2:

    A reference for the famously demonstrated correlations in
    globular clusters is needed.

We have added references to: Norris & Da Costa (1995), which (to our
knowledge) was the first to unambiguously show anti- correlations in
Na, Al, and O, and to Carretta et al (2009), which provides a more
recent and comprehensive view of our current knowledge of elemental
abundance correlations in gloublar clusters.

@@

-----
Other changes:

In addition to all the above, we made the following additional
changes:

Because of discussions and checking of results that happened
subsequent to our submission of this paper with the APOGEE team, some
of which made use of proprietary data and information about the
survey, we have expanded the author list in accordance with the
APOGEE/SDSS-III authorship policies.  The consequence is that there
are now several additional new authors, most of whom contributed to
this project most directly by building the APOGEE project (and hence
the input data and tests thereof).

We added the two crucial APOGEE references: Eisenstein et al (2011;
SDSS-III) Holtzman et al (2015; APOGEE DR12).

We softened very slightly the "no previous successes" sentence in the
abstract and also cited Majewski et al (2012). We also added a caveat
that globular-cluster members are over-represented in APOGEE because
of targeting decisions.

@@

We fixed a small bug with the cluster density measure and updated the
figure. This changes no conclusions.

We fixed the (embarrassing) bug that everywhere we say "Pal 5" we mean
"M5". This was a straight-up mistake in the paper, and leads to some
changes in the discussion, including some reference changes. No
fundamental conclusions change because of this.

We noted the point (related to the referee's comments) that everything
we find that is dense in phase space is at low metallicity; this is
probably because of our sensitivity to clusters above background (in
abundance space).

### 2016-08-07 papers/kmeans/response_to_referee.txt

    There are some missing references to the original demonstrations
    of chemical tagging of unbound groups, namely the Wolf 630 group
    and HR 1614 group. Those were key to building up the case for
    this "tagging" research.

We have added the following references: De Silva et al (2007), Eggen
(1970), and Bubar & King (2010). Also Helmi et al (2006) and (2014).

    The text needs to highlight that the training set is critical -
    Cannon doesn't know physics. It needs to be told what is "true"
    and that the subsequent results will be limited to the believed
    level of truth. While it should be specified that tagging per se
    doesn't require absolute abundances, but the subsequent
    interpretation of the chemical accretion history will require
    "true" abundances - not just precision. Also some clarification
    about the Cannon's performance at the boundaries of the training
    set parameters would have been good to see.

This statement and point is true and wise. We have added a paragraph
in Section 2 describing and emphasizing this point, and also
addressing the point that The Cannon can use element-element
correlations to improve its precision. All these things reduce the
interpretability of the absolute abundances shown in the paper, as the
referee notes. We refer to the Casey et al paper to see the
performance of the method at the edges.

@@

We have added references to: Norris & Da Costa (1995), which (to our
knowledge) was the first to unambiguously show anti- correlations in
Na, Al, and O, and to Carretta et al (2009), which provides a more
recent and comprehensive view of our current knowledge of elemental
abundance correlations in gloublar clusters.

    Section 3:

    The text doesn't clarify why only k-means was chosen to do the
    'tagging' given the issues discussed, was it simply easy and
    fast? Fine as the focus of the paper is the precision of the
    abundance results with Cannon, not the fidelity of group finding.

We have added text to clarify why k-means was chosen. It is
fundamentally because k-means is the clustering algorithm of "first
resort", which contains very few assumptions and only one (integer)
adjustable parameter (not counting the metric on the vector space);
it is also well tested and understood.

### 2016-08-07 papers/kmeans/kmeans.tex
referee comments

@@

Nothing about this algorithm or our choices are particularly
tuned or optimized; this is in no sense the
algorithm or the method that reveals the best structures.
We chose k-means as a simple and tractable approach to identifying
clusters in high dimensional label space. In practice more complex
clustering algorithms may perform better than k-means, or even
tuning k-means by heuristically setting $K$ is likely to improve
upon the results here. This \documentname\ serves as a proof of concept.
Indeed, it is a feature of this work that even the simplest, most
generic clustering algorithm returns interesting
structures (as shown below). 
The prospects for Milky Way science only improve as the clustering
algorithm improves.

>>>>

HOGG: Paragraph here about limitations of \thecannon: Dependence on
training set, makes use of element-element correlations (especially, say, Na),
and delivers precision but no guarantees of accuracy beyond that in the training set.
Comment on its performance at the edges of the abundance distribution...? As per referee issue.

@@

Nothing about this algorithm or our choices are particularly
tuned or optimized; this is in no sense the
algorithm or the method that reveals the best structures.
We chose k-means as a simple and straightforward approach to identifying
clusters in high dimensional label space, with very few control parameters
or decisions required.
It is also an algorithm that is well studied in the machine-learning literature,
so it has well understood properties.
In practice more complex
clustering algorithms may perform better than k-means, or even
tuning k-means by heuristically setting $K$ is likely to improve
upon the results here. This \documentname\ serves as a proof of concept.
Indeed, it is a feature of this work that even the simplest, most
generic clustering algorithm returns interesting
structures (as shown below). 
The prospects for Milky Way science only improve as the clustering
algorithm improves.
